\texttt{davos}: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2022-10-06 paper/main.tex
WIP software architecture section

\subsection{Software architecture}
The \texttt{davos} package is structured as two sub-packages: a set of ``core" modules that implement...

>>>>

\subsection{Software architecture}
The \texttt{davos} package consists of two interdependent subpackages. The first comprises a set of ``core" modules that implement\comment{provide?} much of \texttt{davos}'s major functionality, including machinery for installing and validating packages, custom parsers for the \texttt{smuggle} statement (see Section \ref{subsec:smuggle}) and onion comment (see Section \ref{subsec:onion}), and a runtime interface for configuring \texttt{davos}'s behavior (see Section \ref{subsec:config}). However, certain critical\comment{other important} aspects of this functionality require (often substantially) different implementations depending on various properties of the notebook in which \texttt{davos} is used (e.g., whether the frontend is provided by Jupyter or Google Colaboratory, or which version of IPython \cite{PereGran07} is used by the notebook kernel). To deal with this, environment-dependent parts of core features and behaviors are isolated and abstracted to ``helper functions", which are imported from the ``implementations" subpackage. This second subpackage defines multiple, interchangeable implementations of each helper function, organized into per-environment modules. At runtime, \texttt{davos}
